\documentclass[../paper.tex]{subfiles}
\begin{document}
String Theory is a very complex problem which cannot be solved yet. As a lot of other research in Science, it's also good to try to disprove your hypothesis. Because of some aspects, like the finite amount of possibilities for M and V within M-Theory, it's likely that String Theory can be proven to be false by an experimental approach. In order to achieve this, a strong platform for Computer Sciences needs to be created, which can handle lots of different constructs all together. This platform can be created by using parallel computing in order to do multiple processes with different constructs all at the same time. Currently, scientists are working on String Theory a lot in order to solve this problem and afterwards derive new Laws of Nature and particles from String Theory. However, if proven to be false, finding new approaches for a Theory of Everything could mean other significant progress in the world of Physics. This falsification can be done by computers and could save a lot of people a lot of unnecessary work and money. I personally believe that String Theory contains a very strong framework, especially M-Theory, which could be a great way to find new Laws of Nature and gain more insights into physics. On the otherhand, Arthur Conan Doyle once said:
\begin{quote}
    When you have eliminated all which is impossible, then whatever remains, however improbable, must be the truth.
    \author{Arthur Conan Doyle}
    \label{Deduction}
\end{quote}
This is a purely deductive theory, which is, in my opinion, not only very important to overcome fixed mindsets in general, but also specifically very important for Modern Sciences. The only way to reach the truth, is to trust the facts, no matter how weird, paradoxical or unwished they sound. 
\end{document}